Plots for Latent Hawkes Paper

### 2020-12-01 output_scripts/Paper_Plots.Rmd
WIP, correcting under/over estimation for fig 4b

slides_plots <- FALSE
current_cohort <- 5

@@

@@

colors_plot <- viridis(2)
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
plot(order(expert_rank_10[[current_cohort]]),
     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
     #col= "steelblue",
     col = colors_plot[1],
     ylab="",xlab="",
     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
segments(order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
         order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
         #col= add.alpha("steelblue",0.8),lwd=2)
         col = add.alpha(colors_plot[1],0.8), lwd =2)
points(order(expert_rank_10[[current_cohort]])+0.2,
       apply(sim_cohort_dchp$f,2,mean),
       pch=16,cex=1.2,
       col=colors_plot[2])
       #col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
         order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
         col= add.alpha(colors_plot[2],0.8),lwd=2)
         #col= add.alpha("goldenrod2",0.8),lwd=2)

@@

```{r, eval=FALSE}
par(mar=c(3,3,1,1))
plot(as.vector(n_matrix[n_matrix>0]), as.vector(ks.stat.matrix[n_matrix>0]),
     xlab="", ylab="", pch=16, col="gray", cex= 0.8, xaxt="n", yaxt="n",
     ylim=c(0,0.65))
mtext("Number of events", cex=1.5, side=1, line=1.8)
mtext("K-S statistics", cex=1.5, side=2, line=1.5)
mgp.axis(1,mgp=c(0,0.3,0),at=seq(0,120,10),cex.axis=1,lwd=0,lwd.ticks=0.1)
mgp.axis(2,mgp=c(0,0.1,0),at=seq(-0.2,0.6,0.2),cex.axis=1,lwd=0,lwd.ticks=0.8)
```

# Redone Figure 3

As discussed, it would be interesting to redo figure 3b
to show the lack of fit in model 2 for one specific pair. This can be somewhat
extracted from the diagnostics file.

We actually want the empirical CDF plot here.

```{r fig_3b_update, fig.height=7}
# 2 -> 11 might be good here
# current_cohort <- 5
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

best_i <- top_pairs$initiator[8]
best_j <- top_pairs$recipient[8]

current_i <- best_i #8
current_j <- best_j #2

### then plots ####
# par(mfrow = c(1, 2), oma = c(1, 1, 1, 1),
#      mar = c(2, 3, 2, 1), mgp = c(0.8,0,0))
# layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3))
anno.cex <- 1.3
title.cex <- 2.2
title.line <- 0.5
y.upper <- 20
#### then the corresponding QQ plot ####
load(paste(data_path,cohort_names[current_cohort],
             "/real_diag_four_models_",cohort_names[current_cohort],
             ".RData",sep=''))
Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]]

p <- ppoints(length(Lambda.dc_hawkes.test))
# 100 equally spaced points on (0,1), excluding endpoints
q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE)
# percentiles of the sample distribution
plot(qexp(p),q,
     xlab="",ylab="",xaxt="n",yaxt="n",
     pch=1, cex=1, col=viridis::viridis(1), ylim=c(0,1), xlim=c(0,4.5))
mtext(side = 1, text = "Theoretical", line=1.6, cex=anno.cex)
mtext(side = 2, text = "Empirical", line = 1.2, cex = anno.cex)
mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2)
# Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1)
# Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:1),cex.axis=1,lwd=0,lwd.ticks=1)
qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5)

### Empirical CDF ####

plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE,
     verticals = TRUE, col = viridis::viridis(1), lwd = 2, 
     xlab = "", ylab = "", xaxt = "n", yaxt = "n",
     main = "", col.01line = NULL)
curve(pexp(x,1/mean(Lambda.dc_hawkes.test)),
      min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test),
      ylab = "", xlab = "",
      add = TRUE, lwd = 2)

```{r repeat entire fig2b for model 2}
# current_cohort <- 5

load(paste(data_path,cohort_names[current_cohort],
             "/real_diag_four_models_",cohort_names[current_cohort],
             ".RData",sep=''))

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_dchp$eta_1)
eta2_mean <- mean(sim_cohort_dchp$eta_2)
eta3_mean <- mean(sim_cohort_dchp$eta_3)
f_est <- apply(sim_cohort_dchp$f,2,mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number)
for(k in 1:mice_number){
  for(l in c(1:mice_number)[-k]){
    i<-expert_rank_10[[current_cohort]][k]
    j<-expert_rank_10[[current_cohort]][l]
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0){
      param_mean <- list(lambda0=mean(sim_cohort_dchp$lambda0[,pair]),
                         alpha=model1_fn$alpha.fun(f_est[i],
                                                   f_est[j],
                                                   eta1_mean,
                                                   eta2_mean,
                                                   eta3_mean),
                         beta=mean(sim_cohort_dchp$beta))
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_Lambda <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ ## check length > 2
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                          return_df$recipient == j &
                            return_df$observe.id==cur_win,"event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                            return_df$observe.id==cur_win,"observe.time"]
        Lambda_vec <- uniHawkesCompensator(object = param_mean,
                              events = c(current_event_time,
                                         current_obs_time))
        all_Lambda <- c(all_Lambda,Lambda_vec)
        n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time)
      }
      if(length(all_Lambda)>0){
        ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp",
                                        rate = 1/mean(all_Lambda))$statistic
        Lambda_matrix[i,j][[1]] <- all_Lambda
      }
    }
  }
}

m2_ks <- ks.stat.matrix

# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks.stat.matrix))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
#order(as.vector(ks.stat.matrix),method = "")

####
par(oma = c(6,4,4,1), mar=rep(0,4),
    mgp = c(0, .2, 0))
layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
                    byrow = TRUE),rep(12*12+1,12)), 
       widths=c(rep(1,12),2), heights=rep(1,12))
for(i in expert_rank_10[[current_cohort]]){
  for(j in expert_rank_10[[current_cohort]]){
    if(ks.stat.matrix[i,j]==0){
      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
           axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = 'white')
    }else{
      Lambda.test <- Lambda_matrix[i,j][[1]]
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], 
           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
      plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
           verticals = TRUE, col = "red", lwd = 2)
    }
  }
}
par(mar = c(0,2,0,3),mgp=c(0,0.8,0))

col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),
                            length.out = 100),
                col.vec = viridis(100))

temp <- cLegend(as.vector(ks.stat.matrix))

image(1, col_obj$x.vec,
      matrix(data=col_obj$x.vec, 
             ncol=length(col_obj$x.vec),nrow=1),
      col=col_obj$col.vec,
      xlab="",ylab="",axes=FALSE)
axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
     cex.axis=2.4)

mtext(text=expert_rank_10[[current_cohort]], side=1,
      line=1.8, outer=TRUE, cex=1.8,
      at=1/14*c(1:12)-1/22)
mtext(text = expert_rank_10[[current_cohort]],
      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
      at =1/12*c(12:1)-1/20, las = 2)
mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
      cex = 2.2,
      at=0.45, font=2)

```{r construct ks_diff}
ks_diff <-  (m2_ks - m1_ks)/m1_ks
ks_diff[is.nan(ks_diff)] <- 0
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks_diff))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks_diff))))
#order(as.vector(ks.stat.matrix),method = "")

values <- as.vector(ks_diff)
sorted_vals <- sort(ks_diff)
#match(values,sorted_vals)
col.vec.vir <- vir_cols[match(values,sorted_vals)]

####
par(oma = c(6,4,4,1), mar=rep(0,4),
    mgp = c(0, .2, 0))
layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
                    byrow = TRUE),rep(12*12+1,12)), 
       widths=c(rep(1,12),2), heights=rep(1,12))
for(i in expert_rank_10[[current_cohort]]){
  for(j in expert_rank_10[[current_cohort]]){
    if(ks_diff[i,j]==0){
      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
           axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = 'white')
    }else{
      Lambda.test <- Lambda_matrix[i,j][[1]]
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])

    }
  }
}
par(mar = c(0,2,0,3),mgp=c(0,0.8,0))

col_obj <- list(x.vec = seq(min(as.vector(ks_diff)),max(as.vector(ks_diff)),
                            length.out = 100),
                col.vec = viridis(100))

# temp <- cLegend(as.vector(ks_diff))

image(1, col_obj$x.vec,
      matrix(data=col_obj$x.vec, 
             ncol=length(col_obj$x.vec),nrow=1),
      col=col_obj$col.vec,
      xlab="",ylab="")
# axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1,
#      cex.axis=2.4)

mtext(text=expert_rank_10[[current_cohort]], side=1,
      line=1.8, outer=TRUE, cex=1.8,
      at=1/14*c(1:12)-1/22)
mtext(text = expert_rank_10[[current_cohort]],
      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
      at =1/12*c(12:1)-1/20, las = 2)
mtext(text = "(M2 - M1)/M1", side = 3, line = 1.4, outer = TRUE,
      cex = 2.2,
      at=0.45, font=2)

```{r construct ks diff normalised by num events}
norm_diff <- (m2_ks - m1_ks)#/m1_ks
norm_diff[is.nan(norm_diff)] <- 0
count_mat <- matrix(0, nrow = mice_number, ncol = mice_number)

for(i in expert_rank_10[[current_cohort]]) {
  for(j in expert_rank_10[[current_cohort]]) {
    if( norm_diff[i,j] != 0 ) {
      num_events <- unique_pairs_df %>% 
      filter(initiator == i & recipient == j) %>%
      pull(count)
      # diff[i,j] <- diff[i,j] / num_events
      count_mat[i,j] <- num_events
    }
  }
}

tibble(diff_norm = as.vector(norm_diff),
       events = as.vector(count_mat)) %>%
  filter(events > 0 ) %>%
  ggplot(aes(events,diff_norm)) + geom_point() +
  ylab("M2-M1") +
  theme_minimal()

tibble(diff_norm = as.vector(norm_diff),
       events = as.vector(count_mat)) %>%
  filter(events > 0) %>%
  ggplot(aes(diff_norm)) + 
  geom_histogram() +
  theme_minimal()

```
```{r repeat for residuals}
m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                   "/chp_pr_matrix_",cohort_names[current_cohort],
                   ".RDS",sep=''))

tibble(m1pr = as.vector(m1_pr),
       m2pr = as.vector(m2_pr)) %>%
  mutate(diff = m2pr - m1pr) %>%
  ggplot(aes(diff)) + 
  geom_histogram() +
  labs(x = "M2 PR - M1 PR") +
  theme_minimal()

```{r compute mean decrease in ks-score}
summary(as.vector(m2_ks[m2_ks != 0]))
summary(as.vector(m1_ks[m1_ks != 0]))

t.test(as.vector(m2_ks[m2_ks != 0]), as.vector(m1_ks[m1_ks != 0]))

diff <- as.vector(m2_ks[m2_ks != 0]) - as.vector(m1_ks[m1_ks != 0])

length(which(diff < 0))/length(diff)
summary(diff)
```

This is good because it shows the most active animal, shows that individual
out rate too large for this interaction. Just need to make this more
like the plots in 2b.

>>>>

slides_plots <- FALSE
extra_plots <- FALSE
current_cohort <- 5

@@

```{r creat colour df}
col_df <- tibble(method = c("I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
            "C-HP", "C-DCHP", "True", "C-MMHP"),
            cols = viridis(9))

@@

colors_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP")) %>%
  pull(cols) 
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
plot(order(expert_rank_10[[current_cohort]]),
     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
     #col= "steelblue",
     col = colors_plot[1],
     ylab="",xlab="",
     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
segments(order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
         order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
         #col= add.alpha("steelblue",0.8),lwd=2)
         col = add.alpha(colors_plot[1],0.8), lwd =2)
points(order(expert_rank_10[[current_cohort]])+0.2,
       apply(sim_cohort_dchp$f,2,mean),
       pch=16,cex=1.2,
       col=colors_plot[2])
       #col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
         order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
         col= add.alpha(colors_plot[2],0.8),lwd=2)
         #col= add.alpha("goldenrod2",0.8),lwd=2)

@@

```{r, eval=FALSE, include=FALSE}
par(mar=c(3,3,1,1))
plot(as.vector(n_matrix[n_matrix>0]), as.vector(ks.stat.matrix[n_matrix>0]),
     xlab="", ylab="", pch=16, col="gray", cex= 0.8, xaxt="n", yaxt="n",
     ylim=c(0,0.65))
mtext("Number of events", cex=1.5, side=1, line=1.8)
mtext("K-S statistics", cex=1.5, side=2, line=1.5)
mgp.axis(1,mgp=c(0,0.3,0),at=seq(0,120,10),cex.axis=1,lwd=0,lwd.ticks=0.1)
mgp.axis(2,mgp=c(0,0.1,0),at=seq(-0.2,0.6,0.2),cex.axis=1,lwd=0,lwd.ticks=0.8)
```

<!-- # Redone Figure 3 -->

<!-- As discussed, it would be interesting to redo figure 3b -->
<!-- to show the lack of fit in model 2 for one specific pair. This can be somewhat -->
<!-- extracted from the diagnostics file. -->

<!-- We actually want the empirical CDF plot here. -->

<!-- ```{r fig_3b_update, fig.height=7, include=FALSE, eval=FALSE} -->
<!-- # 2 -> 11 might be good here -->
<!-- # current_cohort <- 5 -->
<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!-- return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
<!-- unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
<!--   dplyr::summarize(count=n(), -->
<!--             observe=list(observe.id), -->
<!--             observe.length=list(observe.time), -->
<!--             no.events=list(no.events))  -->
<!-- top_pairs <- unique_pairs_df %>% arrange(desc(count)) -->

<!-- best_i <- top_pairs$initiator[8] -->
<!-- best_j <- top_pairs$recipient[8] -->

<!-- current_i <- best_i #8 -->
<!-- current_j <- best_j #2 -->

<!-- ### then plots #### -->
<!-- # par(mfrow = c(1, 2), oma = c(1, 1, 1, 1), -->
<!-- #      mar = c(2, 3, 2, 1), mgp = c(0.8,0,0)) -->
<!-- # layout(matrix(1:8,nrow=2,byrow=TRUE),widths=rep(2,4),height=c(3,3)) -->
<!-- anno.cex <- 1.3 -->
<!-- title.cex <- 2.2 -->
<!-- title.line <- 0.5 -->
<!-- y.upper <- 20 -->
<!-- #### then the corresponding QQ plot #### -->
<!-- load(paste(data_path,cohort_names[current_cohort], -->
<!--              "/real_diag_four_models_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->
<!-- Lambda.dc_hawkes.test <- Lambda_dc_hawkes_matrix[current_i,current_j][[1]] -->

<!-- p <- ppoints(length(Lambda.dc_hawkes.test)) -->
<!-- # 100 equally spaced points on (0,1), excluding endpoints -->
<!-- q <- quantile(Lambda.dc_hawkes.test,p=p,na.rm=TRUE) -->
<!-- # percentiles of the sample distribution -->
<!-- plot(qexp(p),q, -->
<!--      xlab="",ylab="",xaxt="n",yaxt="n", -->
<!--      pch=1, cex=1, col=viridis::viridis(1), ylim=c(0,1), xlim=c(0,4.5)) -->
<!-- mtext(side = 1, text = "Theoretical", line=1.6, cex=anno.cex) -->
<!-- mtext(side = 2, text = "Empirical", line = 1.2, cex = anno.cex) -->
<!-- mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2) -->
<!-- # Hmisc::mgp.axis(1,mgp=c(0,0.1,0),at=c(0:5),cex.axis=1,lwd=0,lwd.ticks=1) -->
<!-- # Hmisc::mgp.axis(2,mgp=c(0,0.1,0),at=c(0:1),cex.axis=1,lwd=0,lwd.ticks=1) -->
<!-- qqline(q, distribution=qexp,col="Black", lty=1, lwd=2.5) -->

<!-- ### Empirical CDF #### -->

<!-- plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE, -->
<!--      verticals = TRUE, col = viridis::viridis(1), lwd = 2,  -->
<!--      xlab = "", ylab = "", xaxt = "n", yaxt = "n", -->
<!--      main = "", col.01line = NULL) -->
<!-- curve(pexp(x,1/mean(Lambda.dc_hawkes.test)), -->
<!--       min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test), -->
<!--       ylab = "", xlab = "", -->
<!--       add = TRUE, lwd = 2) -->

<!-- ``` -->

<!-- ```{r repeat entire fig2b for model 2, include=extra_plots, eval=extra_plots} -->
<!-- # current_cohort <- 5 -->

<!-- load(paste(data_path,cohort_names[current_cohort], -->
<!--              "/real_diag_four_models_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->

<!-- load(paste(data_path,cohort_names[current_cohort], -->
<!--            "/cohort_dchp_stan_result_",cohort_names[current_cohort], -->
<!--            ".RData",sep='')) -->
<!-- eta1_mean <- mean(sim_cohort_dchp$eta_1) -->
<!-- eta2_mean <- mean(sim_cohort_dchp$eta_2) -->
<!-- eta3_mean <- mean(sim_cohort_dchp$eta_3) -->
<!-- f_est <- apply(sim_cohort_dchp$f,2,mean) -->
<!-- clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!-- return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
<!-- unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
<!--   dplyr::summarize(count=n(), -->
<!--                    observe=list(observe.id), -->
<!--                    observe.length=list(observe.time), -->
<!--                    no.events=list(no.events)) -->
<!-- unique_observe_win <- unique(return_df[,c("observe.id","observe.time")]) -->

<!-- ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
<!-- n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->
<!-- Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number) -->
<!-- for(k in 1:mice_number){ -->
<!--   for(l in c(1:mice_number)[-k]){ -->
<!--     i<-expert_rank_10[[current_cohort]][k] -->
<!--     j<-expert_rank_10[[current_cohort]][l] -->
<!--     pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
<!--     if(length(pair)>0){ -->
<!--       param_mean <- list(lambda0=mean(sim_cohort_dchp$lambda0[,pair]), -->
<!--                          alpha=model1_fn$alpha.fun(f_est[i], -->
<!--                                                    f_est[j], -->
<!--                                                    eta1_mean, -->
<!--                                                    eta2_mean, -->
<!--                                                    eta3_mean), -->
<!--                          beta=mean(sim_cohort_dchp$beta)) -->
<!--       current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--       all_Lambda <- numeric(0) -->
<!--       for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
<!--         cur_win <- current_window_vec[cur] -->
<!--         current_event_time <- return_df[return_df$initiator==i& -->
<!--                                           return_df$recipient == j & -->
<!--                             return_df$observe.id==cur_win,"event.times"][[1]] -->
<!--         current_obs_time <- return_df[return_df$initiator==i& -->
<!--                                         return_df$recipient==j& -->
<!--                             return_df$observe.id==cur_win,"observe.time"] -->
<!--         Lambda_vec <- uniHawkesCompensator(object = param_mean, -->
<!--                               events = c(current_event_time, -->
<!--                                          current_obs_time)) -->
<!--         all_Lambda <- c(all_Lambda,Lambda_vec) -->
<!--         n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time) -->
<!--       } -->
<!--       if(length(all_Lambda)>0){ -->
<!--         ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp", -->
<!--                                         rate = 1/mean(all_Lambda))$statistic -->
<!--         Lambda_matrix[i,j][[1]] <- all_Lambda -->
<!--       } -->
<!--     } -->
<!--   } -->
<!-- } -->

<!-- m2_ks <- ks.stat.matrix -->

<!-- # -------------- KS plot (stat) -->
<!-- col.vec <- cRamp(as.vector(ks.stat.matrix)) -->
<!-- ## need to do some sort of transformation between these here -->
<!-- vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix)))) -->
<!-- #order(as.vector(ks.stat.matrix),method = "") -->

<!-- values <- as.vector(ks.stat.matrix) -->
<!-- sorted_vals <- sort(ks.stat.matrix) -->
<!-- #match(values,sorted_vals) -->
<!-- col.vec.vir <- vir_cols[match(values,sorted_vals)] -->

<!-- #### -->
<!-- par(oma = c(6,4,4,1), mar=rep(0,4), -->
<!--     mgp = c(0, .2, 0)) -->
<!-- layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12,  -->
<!--                     byrow = TRUE),rep(12*12+1,12)),  -->
<!--        widths=c(rep(1,12),2), heights=rep(1,12)) -->
<!-- for(i in expert_rank_10[[current_cohort]]){ -->
<!--   for(j in expert_rank_10[[current_cohort]]){ -->
<!--     if(ks.stat.matrix[i,j]==0){ -->
<!--       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="",  -->
<!--            axes = FALSE, frame=TRUE) -->
<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
<!--            border = 0, col = 'white') -->
<!--     }else{ -->
<!--       Lambda.test <- Lambda_matrix[i,j][[1]] -->
<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
<!--             ylab="",xlab="",axes = FALSE, frame=TRUE) -->
<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],  -->
<!--            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)]) -->
<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
<!--             ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2) -->
<!--       plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE, -->
<!--            verticals = TRUE, col = "red", lwd = 2) -->
<!--     } -->
<!--   } -->
<!-- } -->
<!-- par(mar = c(0,2,0,3),mgp=c(0,0.8,0)) -->

<!-- col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)), -->
<!--                             length.out = 100), -->
<!--                 col.vec = viridis(100)) -->

<!-- temp <- cLegend(as.vector(ks.stat.matrix)) -->

<!-- image(1, col_obj$x.vec, -->
<!--       matrix(data=col_obj$x.vec,  -->
<!--              ncol=length(col_obj$x.vec),nrow=1), -->
<!--       col=col_obj$col.vec, -->
<!--       xlab="",ylab="",axes=FALSE) -->
<!-- axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1, -->
<!--      cex.axis=2.4) -->

<!-- mtext(text=expert_rank_10[[current_cohort]], side=1, -->
<!--       line=1.8, outer=TRUE, cex=1.8, -->
<!--       at=1/14*c(1:12)-1/22) -->
<!-- mtext(text = expert_rank_10[[current_cohort]], -->
<!--       side = 2, line = 0.5, outer = TRUE, cex = 1.8, -->
<!--       at =1/12*c(12:1)-1/20, las = 2) -->
<!-- mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE, -->
<!--       cex = 2.2, -->
<!--       at=0.45, font=2) -->

<!-- ``` -->

<!-- ```{r construct ks_diff} -->
<!-- ks_diff <-  (m2_ks - m1_ks)/m1_ks -->
<!-- ks_diff[is.nan(ks_diff)] <- 0 -->
<!-- # -------------- KS plot (stat) -->
<!-- col.vec <- cRamp(as.vector(ks_diff)) -->
<!-- ## need to do some sort of transformation between these here -->
<!-- vir_cols <- viridis::viridis(length((as.vector(ks_diff)))) -->
<!-- #order(as.vector(ks.stat.matrix),method = "") -->

<!-- values <- as.vector(ks_diff) -->
<!-- sorted_vals <- sort(ks_diff) -->
<!-- #match(values,sorted_vals) -->
<!-- col.vec.vir <- vir_cols[match(values,sorted_vals)] -->

<!-- #### -->
<!-- par(oma = c(6,4,4,1), mar=rep(0,4), -->
<!--     mgp = c(0, .2, 0)) -->
<!-- layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12,  -->
<!--                     byrow = TRUE),rep(12*12+1,12)),  -->
<!--        widths=c(rep(1,12),2), heights=rep(1,12)) -->
<!-- for(i in expert_rank_10[[current_cohort]]){ -->
<!--   for(j in expert_rank_10[[current_cohort]]){ -->
<!--     if(ks_diff[i,j]==0){ -->
<!--       plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="",  -->
<!--            axes = FALSE, frame=TRUE) -->
<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
<!--            border = 0, col = 'white') -->
<!--     }else{ -->
<!--       Lambda.test <- Lambda_matrix[i,j][[1]] -->
<!--       curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test), -->
<!--             ylab="",xlab="",axes = FALSE, frame=TRUE) -->
<!--       rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], -->
<!--            border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)]) -->

<!--     } -->
<!--   } -->
<!-- } -->
<!-- par(mar = c(0,2,0,3),mgp=c(0,0.8,0)) -->

<!-- col_obj <- list(x.vec = seq(min(as.vector(ks_diff)),max(as.vector(ks_diff)), -->
<!--                             length.out = 100), -->
<!--                 col.vec = viridis(100)) -->

<!-- # temp <- cLegend(as.vector(ks_diff)) -->

<!-- image(1, col_obj$x.vec, -->
<!--       matrix(data=col_obj$x.vec,  -->
<!--              ncol=length(col_obj$x.vec),nrow=1), -->
<!--       col=col_obj$col.vec, -->
<!--       xlab="",ylab="") -->
<!-- # axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1, -->
<!-- #      cex.axis=2.4) -->

<!-- mtext(text=expert_rank_10[[current_cohort]], side=1, -->
<!--       line=1.8, outer=TRUE, cex=1.8, -->
<!--       at=1/14*c(1:12)-1/22) -->
<!-- mtext(text = expert_rank_10[[current_cohort]], -->
<!--       side = 2, line = 0.5, outer = TRUE, cex = 1.8, -->
<!--       at =1/12*c(12:1)-1/20, las = 2) -->
<!-- mtext(text = "(M2 - M1)/M1", side = 3, line = 1.4, outer = TRUE, -->
<!--       cex = 2.2, -->
<!--       at=0.45, font=2) -->

<!-- ``` -->

<!-- ```{r construct ks diff normalised by num events} -->
<!-- norm_diff <- (m2_ks - m1_ks)#/m1_ks -->
<!-- norm_diff[is.nan(norm_diff)] <- 0 -->
<!-- count_mat <- matrix(0, nrow = mice_number, ncol = mice_number) -->
